Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-02-06 ms.tex
using same stellar spectrum as vivien

We show the measured transmission spectrum in Figure,\ref{fig:tspec}.  The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the planet-to-star flux ratio and subtract it from the transit depth. We calculate planet-to-star flux assuming a FIXME PHOENIX model for the star, a blackbody for the planet, and a planet-to-star radius ratio of FIXME. We consider two plausible nightside temperatures (1400 and 2000 K), which encompass the range of mean nightside temperatures calculated from the phase variation models (Table\,\ref{tab:FIXME}). We also show the uncorrected transit depths. For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of about 10 atmospheric scale heights, much larger than expected from theoretical models. FIXME show GCM in this figure. Water abundance?

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
\caption{The transmission spectrum of WASP-103b (points) for a range of assumptions about the planet's nightside temperature. The gray points correspond to no correction for the nightside flux. The blue and red points assume the average nightside photospheric temperature is 1400 and 2000 K, respectively. The atmospheric scale height assumes FIXME.}
\label{fig:tspec}
\end{figure}

@@

\subsection{Blackbody Fits}
A blackbody is the simplest model for the planet's thermal emission and provides a useful first evaluation of the atmospheric properties. To calculate the best fit blackbody model, we assumed a planet-to-star radius ratio of 0.1063 and used a NEXTGEN (FIXME) stellar spectrum with effective temperature 6110 K.  The best-fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}. This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$. At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data. For phases $0.2 - 0.6$, the \Spitzer\ eclipse depths are significantly larger than predicted for the best fit blackbody, suggesting the presence of an emission feature (due to CO, as we discuss in \S\,\ref{sec:retrieval}). On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature. These differences indicate changes in thermal structure with longitude in the atmosphere.

@@

\begin{deluxetable}{LLL}
	\tablecolumns{3}
	\tablewidth{0pt}
	\tablecaption{Phase-resolved Brightness Temperature \label{table:teffs}}
	\tablehead{
	\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$\tablenotemark{1}} & \colhead{$\chi^2_\nu$}}
		\startdata
		0.06 - 0.15 & 1917 \pm 43 & 0.7 \\
		0.15 - 0.25 & 2254 \pm 25 & 0.8 \\
		0.25 - 0.35 & 2650 \pm 17 & 1.4 \\
		0.35 - 0.44 & 2905 \pm 11 & 1.1 \\
		0.44 - 0.56 & 3011 \pm 8 & 2.4 \\
		0.56 - 0.65 & 2884 \pm 11 & 1.7 \\
		0.65 - 0.75 & 2634 \pm 16 & 1.1 \\
		0.75 - 0.85 & 2312 \pm 23 & 1.2 \\
		0.85 - 0.94 & 2025 \pm 34 & 0.5 \\
		\enddata
		\vspace{-0.8cm}
		\tablenotetext{1}{Brightness temperatures were fit using the WFC3 data only.}
	\end{deluxetable}

>>>>

We show the measured transmission spectrum in Figure,\ref{fig:tspec}.  The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the planet-to-star flux ratio and subtract it from the transit depth. We calculate planet-to-star flux assuming a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1063. We consider two plausible nightside temperatures (1400 and 2000 K), which encompass the range of mean nightside temperatures calculated from the phase variation models (Table\,\ref{tab:FIXME}). We also show the uncorrected transit depths. For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of about 10 atmospheric scale heights, much larger than expected from theoretical models. FIXME show GCM in this figure. Water abundance?

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
\caption{The transmission spectrum of WASP-103b (points) for a range of assumptions about the planet's nightside temperature. The gray points correspond to no correction for the nightside flux. The blue and red points are the corrected for an average nightside photospheric temperature is 1400 and 2000 K, respectively. The atmospheric scale height assumes FIXME.}
\label{fig:tspec}
\end{figure}

@@

\subsection{Blackbody Fits}
A blackbody is the simplest model for the planet's thermal emission and provides a useful first evaluation of the atmospheric properties. To calculate the best fit blackbody model, we assumed a planet-to-star radius ratio of 0.1063 and used a NextGen stellar spectrum interpolated to an effective temperature of 6110 K \citep{allard12}.  The best-fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}. This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$. At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data. For phases $0.2 - 0.6$, the \Spitzer\ eclipse depths are significantly larger than predicted for the best fit blackbody, suggesting the presence of an emission feature (due to CO, as we discuss in \S\,\ref{sec:retrieval}). On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature. These differences indicate changes in thermal structure with longitude in the atmosphere.

@@

\begin{deluxetable}{LLLLL}
	\tablecolumns{5}
	\tablewidth{0pt}
	\tablecaption{Phase-resolved Brightness Temperatures \label{table:teffs}}
	\tablehead{
		\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$\chi^2_\nu$}\tablenotemark{1} \\
	\colhead{\,} & \colhead{WFC3} & \colhead{Ch. 1} & \colhead{Ch. 2} & \colhead{(9 dof)}}
		\startdata
		0.06 - 0.15 & 1917 \pm 43 & 1674 \pm 177 & 1677 \pm 102 & 0.7 \\
		0.15 - 0.25 & 2254 \pm 25 & 2821 \pm 136 & 2486 \pm 87 & 0.8 \\
		0.25 - 0.35 & 2650 \pm 17 & 3170 \pm 128 & 2772 \pm 74 & 1.4 \\
		0.35 - 0.44 & 2905 \pm 11 & 3016 \pm 128 & 3216 \pm 68 & 1.1 \\
		0.44 - 0.56 & 3011 \pm 8 & 3158 \pm 153 & 3350 \pm 53 & 2.4 \\
		0.56 - 0.65 & 2884 \pm 11 & 2764 \pm 133 & 3051 \pm 70 & 1.7 \\
		0.65 - 0.75 & 2634 \pm 16 & 2857 \pm 135 & 2550 \pm 85 & 1.1 \\
		0.75 - 0.85 & 2312 \pm 23 & 2153 \pm 151 & 2117 \pm 91 & 1.2 \\
		0.85 - 0.94 & 2025 \pm 34 & 1825 \pm 167 & 1414 \pm 113 & 0.5 \\
		\enddata
		\tablenotetext{1}{$\chi^2_\nu$ values are for the fits to the WFC3 data only.}
	\end{deluxetable}
